\sysfull

### 2018-08-05 paper/asplos19/paging.tex
Page Faults and Page Swapping revised

non-volatile memory into a \emph{virtual address} in the page buffer in

@@

accesses the protected variable's location in the volatile paging buffer

@@

the pages currently resident in the paging buffer. When a task accesses a

@@

requires \sys to swap out one of the pages in the volatile buffer (a

@@

locations in the main memory \texttt{\underline{store}}. If a task were allowed

>>>>

non-volatile memory into a \emph{virtual address} in \texttt{working} buffer in

@@

accesses the protected variable's location in the volatile \texttt{working} buffer

@@

the pages currently resident in the \texttt{working} buffer. When a task accesses a

@@

requires VMM to swap out one of the pages in the \texttt{working} buffer (a

@@

locations in the main memory \texttt{\underline{private}}. If a task were allowed
